The Implications of Local Fluctuations in the Galactic Midplane for Dynamical Analysis in the \textit{Gaia} Era

### 2019-08-08 paper/ms.tex
Add zenodo doi

\subsection*{Supplementary Material}
All code used in this work is available at:
\url{https://github.com/gusbeane/actions_systematic}.

>>>>

\subsection*{Supplementary Material}
All code used in this work is available at
\url{https://github.com/gusbeane/actions_systematic} and archived at Zenodo
[doi:10.5281/zenodo.3364082].
